Endogenous Politics and the Design of Trade Institutions\thanks{I thank Kyle Bagwell, Mostafa Beshkar, Rick Bond, Chad Bown, Nuno Limao, Giovanni Maggi, Anson Soderbery, Bob Staiger, Maurizio Zanardi, Ben Zissimos and participants in seminars at SITE for very helpful comments and discussions.}

### 2016-12-31 to-do.tex
add new work on GH94/MRC07 to to-do

>>>>

		\item Comparison to GH94
				\item It's the truthful contribution schedule in GH94 that implies the constant weighting of $1+a$ for sectors represented by a lobby. Won't get this clean, constant weighting with other schedules.
				\item Gov't doesn't care about \textit{anything} because it gets the same payoff no matter what
						\item With one lobby, this lobby-has-all-the-bargaining-power feature is an equilibrium implication of the menu-auction set-up where the lobby makes a TIOLI offer
						\item Gov't gets all the surplus when there are two or more lobbies
						\item This result holds in DGH97, p. 767. Footnote 10 explicitly says that this is because lobby makes TIOLI offer.
						\item So go to MRC07 where bargaining power can be manipulated
				\item Menu auction eqm requirement: $(C(\tau),\tau)$ must maximize joint surplus
						\item NB: $\tau$ that maximizes gov't welfare doesn't generically maximize joint surplus (unless it also maximizes lobby payoff)
						\item Careful of transferable vs. non-transferable utility
				\item Not sure if contingent vs. non-contingent payments are a big deal
		\item MRC07
				\item Need case of fixed capital ($z=0$)
				\item NB (p. 1391): optimal trade agreement if lobbies have all the bargaining power and no ex-ante lobbying is free trade
				\item Shift all bargaining power to gov't. They do this in WP version. Read to see what their result is for $z=0$.
						\item Should have gov't make lobby indifferent and maximize joint surplus. But again, this doesn't necessarily maximize gov't welfare
				\item Then re-do MRC07 with $W(\tau) + g(e)$, and version where I subtract $e$
